\makeglossaries

\newglossaryentry{c}{
    name=C,
    description={A high-level general-purpose programming language. Programs written in this language needs to be compiled but can be optimized based on targetted hardware}
}
\newglossaryentry{gammu}{
    name=gammu,
    description={A programming library to easily interface with GSM devices \cite{gammu}}
}
\newglossaryentry{gnss}{
    name=GNSS,
    description={Global Navigation Satellite System.
        A navigation system which provides autonomous geo-spatial positioning on a global coverage.
        This uses satellite constellations such as GPS (USA), GLONASS (Russia), Beidou (China), Galileo (EU), INRSS (India) and QZSS (Japan) \cite{GNSS}}
}
\newglossaryentry{gsm}{
    name=GSM,
    description={Global System for Mobile Communication.
        A wireless communication system which enables exchanging of Short Message Service (SMS) text messages between mobile devices \cite{GSM}}
}
\newglossaryentry{gtk}{
    name=GTK,
    description={An open-source library used for creating graphical user interface \cite{gtk}}
}
\newglossaryentry{heavyequipment}{
    name=Heavy Equipment,
    description={Machineries used in mining operations that are mostly utilized in the loading of ores.
    Compared to light equipment, heavy equipment are mostly static in location.}
}
\newglossaryentry{iot}{
    name=Internet of Things (IoT),
    description={A network of electronic devices with seamless communication with each other \cite{IoT}}
}
\newglossaryentry{microplastics}{
    name=microplastics,
    description={Plastic particles with sizes of less than 5 millimeters \cite{Microplastic}}
}
\newglossaryentry{pms}{
    name=PMS,
    description={Preventive Maintenance Schedule.
        This is a program designed to prevent equipment breakdowns and extend the lifespan of equipment through regular maintenance activities such as inspections, cleaning, lubrication, and replacement of worn or damaged parts.
        The schedule is based on the manufacturer's recommendations, operating conditions, and equipment usage}
}
\newglossaryentry{postgis}{
    name=PostGIS,
    description={An extension of PostgreSQL which allows storing and processing geo-spatial data such as points, line strings and polygons \cite{postgis}}
}
\newglossaryentry{postgres}{
    name=PostgreSQL,
    description={An SQL-compliant open-source relational database management system \cite{postgres}}
}
\newglossaryentry{python}{
    name=python,
    description={A modern interpreted general-purpose programming language.
        Unlike C, programs written in this language do not require compilation and are easier to read and debug}
}
\newglossaryentry{rpi}{
    name={Raspberry Pi},
    description={A low-cost single-board computer with a processor similar to smart phones}
}
\newglossaryentry{smr}{
    name=SMR,
    description={Service Meter Run.
        Number of hours or kilometers that the equipment has operated}
}
\newglossaryentry{database}{
    name={Relational Database},
    description={A collection of tabular data wherein one table can be related to one or more tables}
}
\newglossaryentry{sql}{
    name=SQL,
    description={Structured Query Language.
        This is used in programming and managing data stored in a relational database management system}
}
\newglossaryentry{tmc}{
    name=TMC,
    description={Taganito Mining Corporation.
        A mining company operating a surface mine situated in Tagantio, Claver, Surigao del Norte, Philippines}
}